Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex
OpenStack description

\subsection{OpenStack}
\label{sec:openstack}
\begin{itemize}
\item Descripcion basica del openstack (Sisco?)
\end{itemize}

>>>>

\subsection{OpenStack}
\label{sec:openstack}

One of the most prominent open-source cloud computing platform for both private and public clouds is OpenStack. The OpenStack project was announced in 2010 by Rackspace and NASA, and currently developed and distributed by the OpenStack Foundation with the support of more than 150 relevant companies. OpenStack is a cloud operating system that provides Infrastructure as a Service (IaaS) able to control large pools of compute, storage, and networking resources throughout a datacenter, all managed through a dashboard or an API that gives administrators control while empowering their users to provision resources through a web interface or a command-line.
